\chapter{ACKNOWLEDGMENTS}
I would like to express my deepest thanks to my advisor, James Allan, for his immense support and guidance throughout my PhD study. I especially thank James for giving me lots of freedom in research, which makes the years of PhD study a very enjoyable journey. 

I thank my committee members, Bruce Croft, David Jensen and Micheal Lavine, for their valuable feedback. I also thank Bruce for his influence on our lab that I have enjoyed, David for influencing me in conducting scientific research, Micheal for his inspiration on part of this thesis. I thank all other research scientists who helped me specifically on this thesis work, including Zhicheng Dou from Microsoft Research Asia, David Smith, Henry Field, Limi Yao and Bo Jiang from UMass Amherst.

I would like to thank all other mentors and friends who helped me in my past research career. I especially thank Yiqun Liu for introducing me to research when I was an undergraduate student. I thank Elif Aktolga for her help in my earlier years of the PhD study. I thank Rui Li, Roger Jie Luo and Yi Chang, who mentored me during my time at Yahoo! Labs. 

I thank all staffs of our lab, Kate Morruzzi, Dan Parker, Jean Joyce and Glenn Stowell for their incredible support, which makes it possible for me to enjoy research work and not worry about others. I also thank our Graduate Program Manager, Leeanne Leclerc, for her help throughout this PhD program.

I thank all my friends and colleagues in our lab for sharing various ideas about research, and life as well. In alphabetical order: Qingyao Ai, Elif Aktolga, Michael Bendersky, Keping Bi, Jie Bing, Ethem Can, Marc Cartright, Daniel Cohen, Jeffery Dalton, Van Dang, Laura Dietz, Shiri Dori-Hacohen, Henry Feild, David Fisher, John Foley, Jiafeng Guo, Stephen Harding, Samuel Huston, Ashish Jain, Myung-ha Jang, Jiepu Jiang, Mostafa Keikha, Chang Bong Kim, Jin Young Kim, Youngho Kim, Kriste Krstovski, Chia-Jung Lee, Tamsin Maxwell, Venkatesh Narasimha Murthy, Nada Naji, David Novak, Jae Hyun Park, Jangwon Seo,  Manmeet Singh, Ibrahim Uysal, Ziqi Wang, David Wemhoener, Xiaoye Wu, Xiaobing Xue, Zeki Yalniz, Liu Yang, Xing Yi, Xucheng Yin, Hamed Zamani, Michael Zarozinski. I wish them all the best for their future endeavors.

Finally, I would like to thank my parents for their education that encouraged my independent thinking, their support in whatever path I chose to pursue, and their love from the other side of the globe.

This work was supported in part by the Center for Intelligent Information Retrieval, in part by IBM subcontract \#4913003298 under DARPA prime contract \#HR001-12-C-0015 , in part by an award from Google, in part by NSF grant \#IIS-0910884, and in part by UpToDate. Any opinions, findings and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect those of the sponsor.